\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{multicol}

% Define colors
\definecolor{headingcolor}{RGB}{0, 51, 102}
\definecolor{subheadingcolor}{RGB}{70, 130, 180}
\definecolor{accentcolor}{RGB}{70, 130, 180}

% Custom section command
\titleformat{\section}
  {\large\bfseries\color{headingcolor}\uppercase}
  {}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1.2}{*0.4}

% Remove page numbers
\pagenumbering{gobble}

% Custom commands
\newcommand{\name}[1]{
  \begin{center}
    \Huge\textbf{\color{headingcolor}#1}
  \end{center}
  \vspace{-0.5em}
  \hrule height 0.8pt width \textwidth
  \vspace{0.5em}
}
\newcommand{\contact}[3]{
  \begin{center}
    \faEnvelope\ #1 \hspace{1em} \faPhone\ #2 \hspace{1em} \faMapMarker*\ #3
  \end{center}
  \vspace{-0.5em}
  \hrule height 0.4pt width \textwidth
  \vspace{0.5em}
} 
\newcommand{\role}[4]{
  \textbf{\color{subheadingcolor}#1} \hfill \textbf{#2} \\
  \textit{#3} \hfill \textit{#4}
}

\begin{document}

\name{Joe H Hollander}
\vspace{-0.25em}
\contact{joe.h.hollander@gmail.com}{(802) 233-0910}{185 Rye Circle, South Burlington, VT 05403}

\vspace{-0.25em}
\begin{center}
\textit{Enthusiastic and reliable high school student who enjoys working with others, creating positive experiences, and delivering excellent customer service. Always timely, responsible, and motivated to bring energy and a smile to the workplace.}
\end{center}

\vspace{2em}
\section{EXPERIENCE}
\vspace{0.5em}

\begin{flushleft}
  \textbf{\color{subheadingcolor}DUAL ENROLLMENT AMBASSADOR — University of Vermont}
  \begin{itemize}[leftmargin=*,nosep,itemsep=3pt]
      \item Marketed UVM's dual enrollment program to prospective students through TikTok and in-person events.
      \item Achieved \textbf{over 1.5 million} views and \textbf{2,900} likes on TikTok.
      \item Coordinated and led on-site promotional activities at South Burlington High School.
  \end{itemize}
\end{flushleft}

\begin{flushleft}
  \textbf{\color{subheadingcolor}FRONT DESK STAFF — Farpost Soccer Club}
  \begin{itemize}[leftmargin=*,nosep,itemsep=3pt]
      \item Welcomed players, families, and guests with a positive attitude.
      \item Managed scheduling, inventory, and cleaning to ensure smooth day-to-day operations. 
      \item Dealt with inquiries, concerns, and feedback from players and parents.
      \item Supported coaches and referees.
  \end{itemize}
\end{flushleft}

\begin{flushleft}
  \textbf{\color{subheadingcolor}SOCCER REFEREE — Vermont Soccer Association}
  \begin{itemize}[leftmargin=*,nosep,itemsep=3pt]
      \item Refereed over \textbf{350} hours of soccer games (U10–U19), ensuring fairness and respect on the field. 
      \item Resolved conflicts calmly and professionally while maintaining a fun, safe atmosphere. 
      \item Demonstrated responsibility and punctuality at all scheduled games. 
  \end{itemize}
\end{flushleft}

\vspace{2em}
\section{SKILLS}
\vspace{0.5em}
\begin{itemize}[leftmargin=*,nosep,itemsep=5pt]
  \item \textbf{Customer Service:} Friendly, Conflict Resolution, Problem Solving 
  \item \textbf{Teamwork:} Leadership, Collaboration, Communication 
  \item \textbf{Responsibility:} Punctuality, Reliability, Organization
  \item \textbf{Administrative:} Scheduling, Inventory
\end{itemize}

\vspace{2em}
\section{EDUCATION}
\vspace{0.5em}
\role{South Burlington High School}{South Burlington, VT}{Current GPA: 3.99/4.00}{August 2022--Present}   

\vspace{2em}
\section{EXTRACURRICULAR ACTIVITIES}
\vspace{0.5em}

\begin{itemize}[leftmargin=*,nosep,itemsep=5pt]
  \item Math League Champions (2022–2025), Captain (2025)
  \item Ping Pong Club President (2024–2025)
  \item Varsity Soccer (2024-25)
  \item Varsity Ultimate Frisbee (2024–2025)
  \item Club Soccer (2017–2025), Captain (2025)
  \item Math Tutoring ($\sim$35 hours)
\end{itemize}

\end{document}
